A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-02-01 papers/execution-model/model.tex
Add files via upload

\author{Doan Thi Thu Ha \and
Peter Thiemann\orcidID{0000-0002-9000-1239}}
\institute{University of Freiburg, Germany\\
\email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
}

@@

Although closing contract and bidding strategy tasks are not able to be implemented in a smart contract, they could be in programs that interact with the blockchain. We call the function that deploy a contract \texttt{originate-contract}, and  it results the contract's address on the blockchain.  The function that invokes a contract is \texttt{call-contract}. The \texttt{get-state} function queries data on the blockchain and returns the storage of a contract. The owner could first deploy the contract, waitg 48 hours, and then call the contract with the entrypoint \texttt{Unit} to close the contract.

\begin{lstlisting}[numbers=none]
address = orinigate-contract(script);
Time.sleep(to-second(48));
call-contract(address, Unit);
\end{lstlisting}

>>>>

\author{Thi Thu Ha Doan\and
Peter Thiemann\orcidID{0000-0002-9000-1239}}
\institute{University of Freiburg, Germany\\
\email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
}

@@

Although contract closing  and bidding strategy tasks are not able to be implemented in a smart contract, they could be in programs that interact with smart contracts on the blockchain. We call the function that deploys a contract \texttt{originate-contract}, and  it returns the contract's address on the blockchain.  The function that invokes a contract is \texttt{call-contract}. \texttt{get-state} function queries data on the blockchain and returns the storage of a contract. The owner could first deploy the contract, wait 48 hours, and then call the contract with the entrypoint \texttt{Unit} to close the contract.

\begin{lstlisting}[numbers=none]
address = orinigate-contract(script);
Time.sleep(to-second(48));
call-contract(address, Unit);
\end{lstlisting}
where \texttt{script} is the contract's script and \texttt{to-second} function converts hour to second.
